---
title: "Using knitractive with Python"
author: "Jeroen Janssens"
date: "`r Sys.Date()`"
output: github_document
---

*View the corresponding [python.Rmd file](https://raw.githubusercontent.com/datascienceworkshops/knitractive/master/vignettes/examples/python.Rmd) to learn more about how this page was generated.*

```{r setup, include = FALSE}
library(knitractive)
library(rexpect)
library(rlang)
start(name = "python",
      command = cmd_docker(command = "python3",
                           image = "continuumio/anaconda3",
                           volume = list2(!!getwd() := "/data")),
      prompt = prompts$python,
      keep_session = FALSE)
```

In this example, we're using the [continuumio/anaconda3](https://hub.docker.com/r/continuumio/anaconda3/) docker image to run Python.

```{python}
import numpy as np
import pandas as pd
import matplotlib
Enter#! literal = FALSE
matplotlib.use('agg')
pd.__version__
```

Because `knitractive` employs the [tmuxr](https://datascienceworkshops.github.io/tmuxr/) package under the hood, the python session is maintained, and we can continue where we left off.

```{python}
ts = pd.DataFrame({"value": np.random.randn(1000)},
                  index=pd.date_range('1/1/2000',
                  periods=1000))
ts = ts.cumsum()
ts.head()#! enter = FALSE, expect_prompt = FALSE
```

```{python, include = FALSE}
C-c#! literal = FALSE, expect_prompt = TRUE
ts.head().to_html("/data/python_ts.html", border=0)
```

```{r, echo = FALSE}
htmltools::includeHTML("python_ts.html")
unlink("python_ts.html")
```

We've mapped the current working directory on the host to the directory `/data/` inside the docker container, so that we can include generated figures.

```{python}
ts.plot() #! enter = FALSE, expect_prompt = FALSE
```

```{python, include = FALSE}
C-c #! wait = 0.2, literal = FALSE, expect_prompt = TRUE
ts.plot().figure.savefig("/data/python_ts.png", dpi = 200)
```

```{r, echo = FALSE}
knitr::include_graphics(paste0(getwd(), "/python_ts.png"))
```

*View the corresponding [python.Rmd file](https://raw.githubusercontent.com/datascienceworkshops/knitractive/master/vignettes/examples/python.Rmd) to learn more about how this page was generated.*
